---
title: "Exercise-2"
author: "Serra Aksoy"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

# Exercise 2.1: Linear Regression with Housing Price Prediction

## Load the Dataset
```{r}
housing_data <- read.csv("Housing.csv")
```

## Data Exploration
```{r}
str(housing_data)
summary(housing_data)
```

## Calculate Average Price
```{r}
average_price <- mean(housing_data$price)
paste("The average price of the house is", average_price)
```

## Fit a Linear Regression Model
```{r}
model <- lm(price ~ area + bedrooms + bathrooms + airconditioning,
            data = housing_data)
summary(model)
```

## Evaluate the Model
```{r}
rsq <- summary(model)$r.squared
adj_rsq <- summary(model)$adj.r.squared
paste("R-squared:", rsq)
paste("Adjusted R-squared:", adj_rsq)
```

## Predict Prices
```{r}
predictions <- predict(model, newdata=housing_data[1:10, ])
predictions
housing_data[1:10, 'price']
```

## Residual Analysis
```{r}
plot(model$residuals)
abline(h = 0, col = "red")
```

## Plot Regression Coefficients
```{r}
library(ggplot2)
coeffs <- data.frame(term = names(coef(model)), estimate = coef(model))
ggplot(coeffs, aes(x = term, y = estimate)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = estimate - 1.96*summary(model)$coefficients[,2], ymax = estimate + 1.96*summary(model)$coefficients[,2]))
```

# Exercise 2.2: Logistic Regression with Credit Card Eligibility Data

## Load the Dataset
```{r}
credit_data <- read.csv("dataset.csv")
```

## Data Exploration
```{r}
str(credit_data)
summary(credit_data)
```

## Calculate Median Income
```{r}
median_income <- median(credit_data$Total_income)
credit_data$above_median_income <- ifelse(credit_data$Total_income > median_income, 1, 0)
credit_data$above_median_income
```

## Fit a Logistic Regression Model
```{r}
logistic_model <- glm(Target ~ Age + Num_children + Num_family + Family_status, data = credit_data, family="binomial")
summary(logistic_model)
```

## Evaluate the Model
```{r}
aic <- summary(logistic_model)$aic
deviance <- summary(logistic_model)$deviance
paste("AIC:", aic)
paste("Deviance:", deviance)
```

## Predict Probabilities
```{r}
predicted_probabilities <- predict(logistic_model, newdata=credit_data[1:10, ], type="response")
predicted_probabilities
credit_data[1:10, "Target"]
```

## Plot ROC curve and calculate AUC
```{r}
library(pROC)
roc_curve <- roc(credit_data$Target, predict(logistic_model, type="response"))
plot(roc_curve)
auc(roc_curve)
```

## Confusion Matrix
```{r}
library(caret)
predictions <- ifelse(predicted_probabilities > 0.5, 1, 0)
confusion_matrix <- confusionMatrix(as.factor(predictions), as.factor(credit_data$Target[1:10]))
confusion_matrix

sum(credit_data$Target == 0)
sum(credit_data$Target == 1)
```